\documentclass[runningheads]{llncs}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{xparse}
\usepackage[capitalise,noabbrev]{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{wasysym}
\usepackage{agda}
\usepackage{src/agdadimmed}
% \usepackage{src/agdatheme}
\usepackage{newunicodechar}
\usepackage{mdframed}
\usepackage{wrapfig}
\usepackage{boxedminipage}
\usepackage{dsfont}
\usepackage{etoolbox}
\usepackage{scalerel}
\usepackage{graphicx}
\usepackage{mathbbol}
\usepackage{lineno}


% adjust outrageous indent on itemized lists
\usepackage{enumitem}
\setlist[itemize,1]{leftmargin=\dimexpr 2em}

\makeatletter
\newcommand{\crefnames}[3]{%
  \@for\next:=#1\do{%
    \expandafter\crefname\expandafter{\next}{#2}{#3}%
  }%
}
\patchcmd{\upbracefill}{\m@th}{\scriptstyle\m@th}{}{}
\patchcmd{\upbracefill}{$\braceld$}{$\scriptstyle\braceld$}{}{}
\patchcmd{\upbracefill}{\bracelu}{\bracelu\mkern-1mu}{}{}
\patchcmd{\upbracefill}{\hfill\braceru}{\hfill\mkern-1mu\braceru}{}{}
\makeatother

\crefnames{section}{\S}{\S\S}

\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\tikzset{block/.style={draw, thick, text width=3cm, minimum height=1.5cm, align=center}, line/.style={-latex}}
\usepackage{pgfplots} 

\newtoggle{draft}
\toggletrue{draft} % enables notes

\iftoggle{draft}{
\linenumbers
}

\input{src/macros/todo.tex}

%%
%% Agda typesetting commands shorthands, for
%% manual typesetting of inline code
%%

\newcommand{\af}{\AgdaFunction}
\newcommand{\un}{\AgdaUnderscore}
\newcommand{\ad}{\AgdaDatatype}
\newcommand{\ab}{\AgdaBound}
\newcommand{\ac}{\AgdaInductiveConstructor}
\newcommand{\aF}{\AgdaField}
\newcommand{\as}{\AgdaSymbol}
\newcommand{\aS}{\AgdaString}
\newcommand{\ak}{\AgdaKeyword}
\newcommand{\ap}{\AgdaPrimitiveType}
\newcommand{\an}{\AgdaNumber}
\newcommand{\aC}{\AgdaComment}
\newcommand{\am}{\AgdaModule}


%%
%% Unicode for typesetting Agda code
\input{src/unicode.tex}

%%
% Multi-column code
\NewDocumentCommand{\vcodesep}{}{{\color{lightgray}\vrule}}

% displays put some stuff like code in a paragraph, without interrupting it.
\setlength{\parskip}{0em} 
\setlength\mathindent{0.2cm}
%\setlength\abovedisplayskip{0em}
%\setlength\belowdisplayskip{em}
\usepackage{float}
\newcommand{\displayskip}[1]{%
  {\parskip=0pt\parindent=0pt\par\vskip #1\noindent}}
\NewDocumentCommand{\display}{m}
  {{\ifhmode%
    \parskip=0pt\parindent=0pt\par\vskip 5pt\noindent
    %\displayskip{\abovedisplayskip}%
    %\displayskip{0pt}%
       #1%
    %\displayskip{\belowdisplayskip}%
    \parskip=0pt\parindent=0pt\par\noindent
    \displayskip{0pt}%
   \else
     #1
   \fi}}

\NewDocumentCommand{\twocodes}{O{0.49\textwidth} O{0.49\textwidth} m m}
  {\display{\vskip -10pt
    \begin{minipage}[t]{#1}
    #3
    \end{minipage}
    \hfill\vcodesep
    \begin{minipage}[t]{#2}
    #4
    \end{minipage}
  }}

\pagestyle{plain}

% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
% \usepackage{color}
% \renewcommand\UrlFont{\color{blue}\rmfamily}
% \urlstyle{rm}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Effects with Variable Binding}

\author{Anonymous}

\maketitle

\begin{abstract}
Algebraic effects let programmers declare the syntax of operations which can be used to write and compose effectful programs.
Such programs can be run by applying effect handlers that give programmers control over when and how many times to call continuations of operations.
Embedding algebraic effects and handlers in an existing language provides a lightweight and powerful approach to programming with effects.
Such embeddings typically use host language functions to represent continuations of programs.
While host language functions offer an ergonomic interface for programming with and handling effects, they also hinder programmers wishing to define custom optimizations for effectful programs.
Specifically, optimizations that statically analyze and transform variable bindings cannot be defined, as that would require meta-programming facilities for host language functions.

This paper presents a solution to this problem by embedding algebraic effects as intrinsically typed, De Bruijn-indexed syntax.
Working in Agda, we demonstrate how this provides a safe-by-construction approach to programming with effects that is almost as ergonomic as the traditional embedding, but which additionally supports optimizations that inspect and transform variable binding.

\keywords{Algebraic Effects \and Variable Binding \and Program Transformation.}
\end{abstract}

\input{src/sections/1-introduction.tex}
\input{src/sections/2-overview.tex}
\input{src/sections/3-syntax.tex}
\input{src/sections/4-sharing.tex}
\input{src/sections/6-case.tex}
\input{src/sections/7-related.tex}
\input{src/sections/8-conclusion.tex}

\begin{credits}
\subsubsection{\ackname} A bold run-in heading in small font size at the end of the paper is
used for general acknowledgments, for example: This study was funded
by X (grant number Y).

\subsubsection{\discintname}
It is now necessary to declare any competing interests or to specifically
state that the authors have no competing interests. Please place the
statement with a bold run-in heading in small font size beneath the
(optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
system, is used, then the disclaimer can be provided directly in the system.},
for example: The authors have no competing interests to declare that are
relevant to the content of this article. Or: Author A has received research
grants from Company W. Author B has received a speaker honorarium from
Company X and owns stock in Company Y. Author C is a member of committee Z.
\end{credits}

\bibliographystyle{splncs04}
\bibliography{src/references}

\end{document}
\endinput